Chasing \rainbows{} with the Habitable Worlds Observatory

### 2023-03-06 src/tex/ms.tex
[showyourwork] overleaf sync

\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
\newcommand{\timmy}[1]{\textcolor{red}{[\textbf{Timmy:} #1]}}

@@

\begin{figure*}
    \centering
    \includegraphics{figures/scatterplot.pdf}
    \caption{
        \todo{Are those the results we obtained for circular, edge-on orbits? 
        We should clarify this also in the figure caption.}
        Scatter plot at 3 $\lambda/D$ for the target sample, showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. 
        The colour of the points shows the atmospheric phenomenon that can be detected with darker colours, including all lighter (yellow) colour phenomenon. 
        Thus, dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
    \script{create-scatterplot.py}
\end{figure*}

@@

\includegraphics[width=\linewidth]{figures/ellipse.pdf}

\timmy{If you agree that this makes sense, I could try to add this to the yarn ball script by Matt?}

@@

>>>>

\newcommand{\todo}[1]{\textcolor{red}{[#1]}}
\newcommand{\timmy}[1]{\textcolor{red}{[\textbf{Timmy:} #1]}} % amazing

@@

\begin{figure*}
    \centering
    \includegraphics{figures/scatterplot.pdf}
    \caption{
        \timmy{I believe those should be the results for circular, edge-on orbits, but let's double-check with Max.}
        Scatter plot at 3 $\lambda/D$ for the target sample, showing stellar effective temperature and stellar distance. 
        The size of the points represents the angular separation of the star and planet in milliarcseconds as presented in the target list. 
        The colour of the points shows the atmospheric phenomenon that can be detected with darker colours, including all lighter (yellow) colour phenomenon. 
        Thus, dark blue points are systems which have the most key features, as systems in which the angles required to see the rainbow are probed will also have the angles required to see the Rayleigh scattering probed.
    }
    \label{fig:scatterplot}
    \script{create-scatterplot.py}
\end{figure*}

@@

\begin{figure}
   \centering
   \includegraphics[width=0.99\columnwidth]{figures/ellipse.pdf}
   \caption{
  Ellipse drawingIf you agree that this makes sense, I could try to add this to the yarn ball script by Matt?    }
    \label{fig:ellipse}
%    \script{plot-orb-grid.py}
\end{figure}

@@

\todo{Sophia: what is features\_plot\_peak.png showing?}

\timmy{Good question --- maybe Matt or Max know how the data for this was generated? (It's not part of the showyourwork yet)}
